---
title: "Purrr Tutorial"
author: "Jonathan Cummings"
date: "April 7, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# load libraries
library(tidyverse)
```

## Purrr Tutorial

This script demonsrates how to use the R tidyverse package purrr. purrr is used to iterate an opperation. 

For more info and notes see: https://docs.google.com/document/d/1ucJiu6QCFu99zeG4U23k-Ve6CHpy-URS3jfCnqd_OP4/edit

### Exercises

#### Exercise 1
The first exercise is to:
a. Compute the mean of columns in mtcars
b. Determine the type of each column in nycflights13::flights.
c. Compute the number of unique values in each column of iris.

```{r cars}
summary(cars)
# Mean of columns in mtcars
map(mtcars,mean) #returns list
map_dbl(mtcars,mean) #returns vector

# Type of columns in nycflights13::flights
map(nycflights13::flights,typeof)

# Count of unique values of iris dataset by column
map(iris,~length(unique(.))) #OR
map(iris,n_distinct)
```

#### Exercise 2
We have data from several years of crab surveys.

The data for each year is contained in separate ".csv" files.

We would like to read these data into R, and combine them into a single data frame so we can inspect and plot them.

```{r crabs}
# Create list of files
files<-dir(path="data/crabs",
           pattern = "*.csv",
           full.names = TRUE)
# Read in files as a dataframe
crab_data<-map_df(files,read_csv) %>% 
  group_by(year, site) %>%
  I()
# plot it
crab_plot <- ggplot(crab_data) +
  aes(x = carcinus, 
      y = cancer, 
      group = site) +
  geom_point() +
  facet_wrap(~site) +
  theme_minimal() +
  NULL
crab_plot

```

#### Exercise 3
We have data on Steller sea lion pup counts over time at a bunch of rookeries in Alaska.

The number of data points for each rookery is not the same.

We want to investigate the annual trend in counts for each rookery.
We want to plot the slopes of the regressions using a histogram.
We want to obtain confidence intervals of the slope estimates using bootstrapping.
```{r sea lions}
# Get sea lion data
ssl <- read_csv("data/SSLpupcounts.csv")
# Convert column names to data in a new column to make a longer table
ssl_long <- ssl %>% 
  pivot_longer(names_to = "year", # column names to a new year column
               values_to = "count", # values in column names_to a count column
               -sitename) %>% # columns to keep as columns
  na.omit()
ssl_long

# plot annual trend

# bootstrapping
ssl_boot <- ssl_models %>%
  mutate(tbl = map(model, augment)) %>% 
  select(sitename, tbl) %>% 
  unnest(cols=c(tbl)) %>% 
  rename("resid" = ".resid") %>% 
  I()
```